Contention Management for 5G

### 2017-02-13 article/article.tex
a

  In this section, we consider a particular case of the model, in which for each $(u,v)$ , the route is the same in both directions. This means that ${\cal R}(u,v)$ uses the same arcs as ${\cal R}(v,u)$ in the opposite orientation.
  \subsection{Intro}
    PALL NP-Hard car PRA NP-Hard\\
    Résultats valables sur Topologie 1 avec nos paramètres
    \todo{J'ai viré star affectation, car je pense qu'il n'y a rien à dire là dessus.}

@@

	\end{algorithmic}
	\end{algorithm}
      \paragraph{Period}
	This algorithm gives us a solution without waiting times in a maximum period $3.\tau.c$, if we have $c$ routes.\\
	Suppose that we have a period of $3.\tau.c$ slots, divided in $\tau$ macro-slots. Let us call {\em forward period} the period in the central node when the messages goes to RRH to BBU, and {\em backward period} the period when the messages comes back in the other way. Put a message in the first slot of size $\tau$ in the forward period, such that the corresponding area in the backward period is free.This message takes at most 2 slots of time $\tau$ in the backward period.\\
      \begin{center}
      \includegraphics[scale=0.2]{ex3nt.png}
      \end{center}
	When $k < c$ messages are put in the forward period, and we want to add another message, there is $3.c - k$ free slots of size $\tau$ in the forward period. Those $3.c - k$ gives us $3.c - k$ possible slots in the backward periods.\\
	The $k$ messages uses at most $2k$ slots of size $\tau$ used in the backward period. Since $k<c$,  $2k < 3.c - k$, thus using the pigeonhole principle, there is at least one free slot in the backward period for the new message.

    \subsubsection{Exhaustive generation}
      Décrire l'algo, expliquer les coupes
    \subsubsection{Results}
      Resultats des simulations : Shortest-longest optimal pour ces parametres.

>>>>

  \subsection{Intro}
    PALL NP-Hard car PRA NP-Hard\\

      In this section, we consider a particular case of the model, in which for each $(u,v)$ , the route is the same in both directions. This means that $\forall (u,v) \in {\cal C}, {\cal R}_{\cal C}(u,v)$ uses the same arcs as ${\cal R}_{\cal C}(v,u)$ in the opposite direction.\\
      Furthermore, the following algorithms and results were designed for a particular topology of network, in which all the routes uses a same common switch.
        \begin{center}
	  \includegraphics[scale=0.8]{Fig4.pdf}
	\end{center}
      Let us call {\bf LN} (leaves node) the central node connected to leaves, and {\bf SN} (sources node), the one connected to sources. The period in those nodes are respectively called {\em forward period}, and {\em backward period}.
      The weight on the link between the two central nodes is simplified in the forthcoming calculations.

@@

	\end{algorithmic}
	\end{algorithm}
      \paragraph{Period}
	This algorithm gives us a solution without waiting times in a maximum period $3.\tau.c$, if we have $c$ routes.\\
	Suppose that we have a period of $3.\tau.c$ slots, divided in $\tau$ macro-slots. Put a message in the first slot of size $\tau$ in the forward period, such that the corresponding area in the backward period is free.This message takes at most 2 slots of time $\tau$ in the backward period.\\
      \begin{center}
      \includegraphics[scale=0.2]{ex3nt.png}
      \end{center}
	When $k < c$ messages are put in the forward period, and we want to add another message, there is $3.c - k$ free slots of size $\tau$ in the forward period. Those $3.c - k$ gives us $3.c - k$ possible slots in the backward periods.\\
	The $k$ messages uses at most $2k$ slots of size $\tau$ used in the backward period. Since $k<c$,  $2k < 3.c - k$, thus using the pigeonhole principle, there is at least one free slot in the backward period for the new message.

    \subsubsection{Exhaustive generation}
	\begin{algorithm}[H]
	\caption{Exhaustive Generation}  
	\begin{algorithmic}
	\REQUIRE A routage graph ${\cal R}_{\cal C}$, period $P$, packet size $\tau$
	\ENSURE $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$
	\STATE Forward-budget $\leftarrow$ $P$ - {\cal c} * $\tau$
	\STATE Backward-budget $\leftarrow$ $P$ - {\cal c} * $\tau$
	\STATE Free-Intervals $\leftarrow$ list of free intervals, init to $[0;P[$
	\FORALL{route i in  ${\cal R}_{\cal C}$}
	\FORALL{j in Free-Intervals }
	\IF{Message of the route i does not collides with scheduled routes}
	\STATE $m_i \leftarrow $ the first slot of Free-Intervals[j]
	\STATE Split the Free-Intervals considering the new packet
	\STATE Forward-budget $\leftarrow$ Forward-budget - {\em lost size}
	\STATE Backward-budget $\leftarrow$ Backward-budget - {\em lost size}
	\STATE call Exhaustive Generation on remaining routes
	\ENDIF
	\ENDFOR
	\ENDFOR

      \end{algorithmic}
      \end{algorithm}
      {\bf {\em Lost size}}, is the size lost when an interval is too few to put another packet. Ex : if the interval [250;3250[ receives a packet of size 2500, there is 500 slots lost, because there is no way to uses the slots for another packet.\\

      This algorithm enumerates all the solutions by traversing a tree. The leaves of the tree are 
      the $(P\tau)$-periodic affectations, and the nodes are partial solutions. A partial solution is a choice of a starting time for a subset of the routes.
      For each route, the algorithm tries every possible starting offset until it finds one available (that allows the message to come back without collisions). When a route have been scheduled, it take another route that have not been scheduled yet.
      This creates a new sub-tree in which the algorithm will try every possible starting offset too, and create a sub-tree on the following route too.
      If no offset are available for a route, this means that the partial solution is not good, so the algorithm backtracks over the tree that is,
      it goes back to the father of the current sub-tree.
      Once a leaf is obtained, the algorithm stops and return the scheduling.\\      
      To reduce the number of useless calculation, in each time we add another packet, we consider the lost size in both periods, thus, we know when a period has no many great enough free area to put a packet.

    \subsubsection{Results}
      Resultats des simulations : Shortest-longest optimal pour ces parametres.
